PANCHANGE_data_preprocessing

### 2020-08-14 PANCHANGE_data_preprocessing2020-07-15.Rmd
adding headers with # no 2

Personality disorder groups
++KT: For all cluster coding chunks - have added other clusters as == 0, so that they are not coerced into NAs. 
Cluster A
1. Paranoid                         28 ( 1.0%)
2. Schizoid                         15 ( 0.5%)
3. Schizotypal                      14 ( 0.5%)
```{r mhd personality_cluster_a}
mhd.raw.id <- mhd.raw.id %>%
  mutate(
    personality_cluster_a_numeric =
      case_when(
        mhd.personality_disorder_diagnosed_numeric == "1" ~ 1,
        mhd.personality_disorder_diagnosed_numeric == "2" ~ 1,
        mhd.personality_disorder_diagnosed_numeric == "3" ~ 1,
        mhd.personality_disorder_diagnosed_numeric == "4" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "5" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "6" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "7" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "8" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "9" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "10" ~ 0,
        mhd.personality_disorder_numeric == "0" ~ 0
      )
  )

@@

Control grouping
These individuals have no self report diagnosis of any kind that we measure. 
```{r mhd control}
mhd.raw.id <- mhd.raw.id %>%
  mutate(
    control_numeric =
      if_else(
    depressive_disorders_numeric == "0" &
    anxiety_disorders_numeric == "0" &
    eating_disorders_numeric == "0" &
    obsessive_compulsive_disorders_numeric == "0" &
    psychotic_disorders_numeric == "0" &
    mhd.mania_hypomania_bipolar_or_manicdepression_numeric == "0" &
    mhd.posttraumatic_stress_disorder_ptsd_numeric == "0" &
    mhd.autism_aspergers_or_autistic_spectrum_disorder_numeric == "0" &
    mhd.attention_deficit_hyperactivity_disorder_numeric == "0" &
    mhd.personality_disorder_numeric == "0", 
    true = 1, 
    false = 0, 
    NA_real_)
  )

@@

Total disorder count
```{r disorders_total_count}
disorder_columns <- c(
    "depressive_disorders_numeric",
    "anxiety_disorders_numeric",
    "eating_disorders_numeric",
    "obsessive_compulsive_disorders_numeric",
    "psychotic_disorders_numeric",
    "mhd.mania_hypomania_bipolar_or_manicdepression_numeric",
    "mhd.posttraumatic_stress_disorder_ptsd_numeric",
    "mhd.autism_aspergers_or_autistic_spectrum_disorder_numeric",
    "mhd.attention_deficit_hyperactivity_disorder_numeric",
    "mhd.personality_disorder_numeric"
)

@@

Comorbidity count
```{r cormorbidity_total_count}
mhd.raw.id <- mhd.raw.id %>%
  mutate(
    comorbidity_total_count_numeric = 
      case_when(
        disorders_total_count == 1 ~ 0,
        disorders_total_count > 1 ~ disorders_total_count - 1
  )
  )

@@

```{r glad mhd head}
head(mhd.raw.id)
```

@@

# exclude cols

>>>>

### Personality disorders
++KT: For all cluster coding chunks - have added other clusters as == 0, so that they are not coerced into NAs. 
Cluster A
1. Paranoid                         28 ( 1.0%)
2. Schizoid                         15 ( 0.5%)
3. Schizotypal                      14 ( 0.5%)
```{r mhd personality_cluster_a}
mhd.raw.id <- mhd.raw.id %>%
  mutate(
    personality_cluster_a_numeric =
      case_when(
        mhd.personality_disorder_diagnosed_numeric == "1" ~ 1,
        mhd.personality_disorder_diagnosed_numeric == "2" ~ 1,
        mhd.personality_disorder_diagnosed_numeric == "3" ~ 1,
        mhd.personality_disorder_diagnosed_numeric == "4" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "5" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "6" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "7" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "8" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "9" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "10" ~ 0,
        mhd.personality_disorder_numeric == "0" ~ 0
      )
  )

@@

### Controls
These individuals have no self report diagnosis of any kind that we measure. 
```{r mhd control}
mhd.raw.id <- mhd.raw.id %>%
  mutate(
    control_numeric =
      if_else(
    depressive_disorders_numeric == "0" &
    anxiety_disorders_numeric == "0" &
    eating_disorders_numeric == "0" &
    obsessive_compulsive_disorders_numeric == "0" &
    psychotic_disorders_numeric == "0" &
    mhd.mania_hypomania_bipolar_or_manicdepression_numeric == "0" &
    mhd.posttraumatic_stress_disorder_ptsd_numeric == "0" &
    mhd.autism_aspergers_or_autistic_spectrum_disorder_numeric == "0" &
    mhd.attention_deficit_hyperactivity_disorder_numeric == "0" &
    mhd.personality_disorder_numeric == "0", 
    true = 1, 
    false = 0, 
    NA_real_)
  )

@@

## Total disorder count
```{r disorders_total_count}
disorder_columns <- c(
    "depressive_disorders_numeric",
    "anxiety_disorders_numeric",
    "eating_disorders_numeric",
    "obsessive_compulsive_disorders_numeric",
    "psychotic_disorders_numeric",
    "mhd.mania_hypomania_bipolar_or_manicdepression_numeric",
    "mhd.posttraumatic_stress_disorder_ptsd_numeric",
    "mhd.autism_aspergers_or_autistic_spectrum_disorder_numeric",
    "mhd.attention_deficit_hyperactivity_disorder_numeric",
    "mhd.personality_disorder_numeric"
)

@@

## Comorbidity count
```{r cormorbidity_total_count}
mhd.raw.id <- mhd.raw.id %>%
  mutate(
    comorbidity_total_count_numeric = 
      case_when(
        disorders_total_count == 1 ~ 0,
        disorders_total_count > 1 ~ disorders_total_count - 1
  )
  )

@@

## Inspection
```{r glad mhd head}
head(mhd.raw.id)
```

@@

# Columns to exclude from add_numeric
